Inference of proto-neutron star properties from gravitational wave data in core-collapse supernovae.

### 2020-10-22 conclusion.tex
Remove Coconut inputs and discussion

Furthermore, the results presented here are based on a model of the frequency evolution of the
ratio that is making use of AENUS-ALCAR code simulations. Using simulations produced
with the CoCoNut code, the model fit is a bit different (see Figure \ref{fig:LMVAR}). This systematic
difference of the two simulation codes is discussed in \cite{Torres:2019b}. If we consider a model based
on CoCoNut simulations and test the method on test simulations obtained with the AENUS-ALACR code,
we observe systematic effects in the ratio reconstruction leading to systematically worsen performance.
As the goal of this paper is to characterize the methods and because both simulation codes have pros
and cons we have reported results obtained with a model set and test set waveforms obtained with the same
code.

>>>>

%Furthermore, the results presented here are based on a model of the frequency evolution of the
%ratio that is making use of AENUS-ALCAR code simulations. Using simulations produced
%with the CoCoNut code, the model fit is a bit different (see Figure \ref{fig:LMVAR}). This systematic
%difference of the two simulation codes is discussed in \cite{Torres:2019b}. If we consider a model based
%on CoCoNut simulations and test the method on test simulations obtained with the AENUS-ALACR code,
%we observe systematic effects in the ratio reconstruction leading to systematically worsen performance.
%As the goal of this paper is to characterize the methods and because both simulation codes have pros
%and cons we have reported results obtained with a model set and test set waveforms obtained with the same
%code.

### 2020-10-22 methods.tex
Update
Remove Coconut inputs and discussion

To build the model of the ratio $r$ as a function of the frequency $f$ we use the 
spherically symetric (1D) simulations of the {\it model set}. Figure~\ref{fig:LMVAR}
shows the data for the $25$ numerical simulations. As identified by \cite{Torres:2019b}, the only systematic
deviation from a single universal relation is the numerical code used in the simulations. 
To avoid any systematic effect, we only use the $18$ simulations performed with the {\sc AENUS-ALCAR}
code, which is the same code that was used in our test set.
%The consequences of this choice are discussed in the conclusions.
Using this data, we parametrize the discretized ratio $r_i$ with a cubic polynomial
regression with heteroscedastic errors
%Here we are using the data from \textcolor{red}{only {\sc AENUS-ALCAR} or both?, maybe colour-code the two groups of data points } to fit a cubic polyn

@@

\begin{figure}
 \centering
 \includegraphics[width=0.5\textwidth]{plots/model}
 \caption{Ratio $M_{\rm PNS}/R_{\rm PNS}^2$ from 25 1D simulations {\sc AENUS-ALCAR} (red) and {\sc CoCoNuT} (green) code. The solid line is the maximum likelihood estimate of heteroscedastic cubic model with 95\% confidence bands (dashed lines) considering \pcd{only} the  {\sc AENUS-ALCAR} data points \pcd{($18$ simulations)}. \mab{To be redone in python}} \label{fig:LMVAR}
\end{figure}

@@

\begin{figure}
 \centering
 \includegraphics[width=0.5\textwidth,height=0.3\textheight]{plots/spectrogram}
 \caption{Spectrogram of the GW signal {\texttt s20S} sampled at \unit[4096]{Hz}.
   The spectrogram is obtained using data streach of 200 samples overlapping at 90\%
   with each other. \mab{To be redone in python}} \label{fig:spectrogram}
\end{figure}

@@

\begin{figure}
 \centering
 \includegraphics[width=0.5\textwidth,height=0.3\textheight]{plots/ratio}
 \caption{Ratio $M_{\rm PNS}/R_{\rm PNS}^2$ as function of time extracted from the $\mbox{}^2 g_2$-mode of the {\texttt s20S} signal (red points and the 95\% confidence belt in grey) compared to the ratio value derived from the PNS mass and radius given by the simulation code (black points) \mab{To be redone in python}.} \label{fig:ratio}
\end{figure}

>>>>

To build the model of the ratio $r$ as a function of the frequency $f$ we use the 
spherically symetric (1D) simulations of the {\it model set}. Figure~\ref{fig:LMVAR}
shows the data for the $25$ numerical simulations. As identified by \cite{Torres:2019b}, the only systematic
deviation from a single universal relation is the numerical code used in the simulations. 
%To avoid any systematic effect, we only use the $18$ simulations performed with the {\sc AENUS-ALCAR}
%code, which is the same code that was used in our test set.
%\mab{We defer a discussion of the possible consequences of this choice in Section \ref{sec:conclusion}.}
%The consequences of this choice are discussed in the conclusions.
Using this data, we parametrize the discretized ratio $r_i$ with a cubic polynomial
regression with heteroscedastic errors
%Here we are using the data from \textcolor{red}{only {\sc AENUS-ALCAR} or both?, maybe colour-code the two groups of data points } to fit a cubic polyn

@@

\begin{figure}
 \centering
 \includegraphics[width=0.5\textwidth]{plots/model}
% \caption{Ratio $M_{\rm PNS}/R_{\rm PNS}^2$ from 25 1D simulations {\sc AENUS-ALCAR} (red) and {\sc CoCoNuT} (green) code. The solid line is the maximum likelihood estimate of heteroscedastic cubic model with 95\% confidence bands (dashed lines) considering \pcd{only} the  {\sc AENUS-ALCAR} data points \pcd{($18$ simulations)}. \mab{To be redone in python}} \label{fig:LMVAR}
 \caption{Ratio $M_{\rm PNS}/R_{\rm PNS}^2$ from 25 1D simulations using {\sc AENUS-ALCAR} code. The solid line is the maximum likelihood estimate of heteroscedastic cubic model with 95\% confidence bands (dashed lines) considering the 18 simulation data points. } \label{fig:LMVAR}

\end{figure}

@@

\begin{figure}
 \centering
 \includegraphics[width=0.5\textwidth]{plots/spectrogram}
 \caption{Spectrogram of the GW signal {\texttt s20S} sampled at \unit[4096]{Hz}.
   The spectrogram is obtained using data streach of 200 samples overlapping at 90\%
   with each other.} \label{fig:spectrogram}
\end{figure}

@@

\begin{figure}
 \centering
 \includegraphics[width=0.5\textwidth]{plots/ratio}
 \caption{Ratio $M_{\rm PNS}/R_{\rm PNS}^2$ as function of time extracted from the $\mbox{}^2 g_2$-mode of the {\texttt s20S} signal (red points and the 95\% confidence belt in grey) compared to the ratio value derived from the PNS mass and radius given by the simulation code (black points).} \label{fig:ratio}
\end{figure}

### 2020-10-22 simulations.tex
Remove Coconut inputs and discussion

{We have used two different numerical codes in our numerical simulations.} 
%CoCoNuT
%(one-dimensional models) and AENUS-ALCAR
%\citep{Just_et_al__2015__mnras__Anewmultidimensionalenergy-dependenttwo-momenttransportcodeforneutrino-hydrodynamics}
%(one- and two-dimensional models). 
CoCoNuT
\citep{Dimmelmeier:2002,Dimmelmeier:2005} is a code for general
relativistic hydrodynamics coupled to the Fast Multigroup Transport
scheme \citep{Mueller_Janka_2015_FMT} providing an approximate
description of the emission and transport of neutrinos. AENUS-ALCAR
\citep{Just_et_al__2015__mnras__Anewmultidimensionalenergy-dependenttwo-momenttransportcodeforneutrino-hydrodynamics}
combines special relativistic (magneto-)hydrodynamics, a modified
Newtonian gravitational potential approximating the effects of general
relativity \citep{Marek_etal__2006__AA__TOV-potential}, and a spectral
two-moment neutrino transport solver
\citep{Just_et_al__2015__mnras__Anewmultidimensionalenergy-dependenttwo-momenttransportcodeforneutrino-hydrodynamics}.
We included the relevant reactions between matter and neutrinos of all
flavours, i.e., emission and absorption by nucleons and nuclei,
electron-positron pair annihilation, nucleonic bremsstrahlung, and
scattering off nucleons, nuclei, and electrons.

@@

{For the {\it test set}, we use $8$ axisymmetric (2D) simulations using the AENUS-ALCAR code
(see Table~\ref{Tab:2dSimList} for a list of models).
$7$ of these simulations use a selection of progenitors with masses in the range} $M_{\mathrm{ZAMS}} = 11.2 - 40 \, \Msol$
 evolved through the hydrostatic phases by
\cite{Woosley_Heger_Weaver__2002__ReviewsofModernPhysics__The_evolution_and_explosion_of_massive_stars}.
We performed one simulation of each stellar model using the equation
of state of \cite{Lattimer_Swesty__1991__NuclearPhysicsA__LS-EOS} with
an incompressibility of $K = 220 \, \mathrm{MeV}$ (LS220) and added
comparison simulations with the SFHo EOS
\cite{Steiner_et_al__2013__apj__Core-collapseSupernovaEquationsofStateBasedonNeutronStarObservations}
and the GShen EOS 
\cite{Shen_et_al__2011__prc__Newequationofstateforastrophysicalsimulations}
for the {progenitor} with $M_{\mathrm{ZAMS}} = 15 \, \Msol$. To this set of
simulations, we add the waveform of a two-dimensional model used in
\cite{Torres:2019a}, denoted \texttt{s20S}. It corresponds to a star
with the same initial mass, $M_{\mathrm{ZAMS}} = 20 \, \Msol$, as for
one of the other 7 axisymmetric simulations, but was taken from a
newer set of stellar-evolution models
\cite{Woosley_Heger__2007__physrep__Nucleosynthesisandremnantsinmassivestarsofsolarmetallicity}.
It was evolved with the SFHo EOS.

>>>>

%{We have used two different numerical codes in our numerical simulations.} 
%CoCoNuT
%(one-dimensional models) and AENUS-ALCAR
%\citep{Just_et_al__2015__mnras__Anewmultidimensionalenergy-dependenttwo-momenttransportcodeforneutrino-hydrodynamics}
%(one- and two-dimensional models). 
%CoCoNuT
%\citep{Dimmelmeier:2002,Dimmelmeier:2005} is a code for general
%relativistic hydrodynamics coupled to the Fast Multigroup Transport
%scheme \citep{Mueller_Janka_2015_FMT} providing an approximate
%description of the emission and transport of neutrinos.
\mab{Both the {\it model set} and {\it test set} simulations have been generated using the numerical
  relativity code AENUS-ALCAR
\citep{Just_et_al__2015__mnras__Anewmultidimensionalenergy-dependenttwo-momenttransportcodeforneutrino-hydrodynamics}
which }combines special relativistic (magneto-)hydrodynamics, a modified
Newtonian gravitational potential approximating the effects of general
relativity \citep{Marek_etal__2006__AA__TOV-potential}, and a spectral
two-moment neutrino transport solver
\citep{Just_et_al__2015__mnras__Anewmultidimensionalenergy-dependenttwo-momenttransportcodeforneutrino-hydrodynamics}.
We included the relevant reactions between matter and neutrinos of all
flavours, i.e., emission and absorption by nucleons and nuclei,
electron-positron pair annihilation, nucleonic bremsstrahlung, and
scattering off nucleons, nuclei, and electrons.

@@

{For the {\it test set}, we use $8$ axisymmetric (2D) simulations using the {\sc AENUS-ALCAR} code
(see Table~\ref{Tab:2dSimList} for a list of models).
$7$ of these simulations use a selection of progenitors with masses in the range} $M_{\mathrm{ZAMS}} = 11.2 - 40 \, \Msol$
 evolved through the hydrostatic phases by
\cite{Woosley_Heger_Weaver__2002__ReviewsofModernPhysics__The_evolution_and_explosion_of_massive_stars}.
We performed one simulation of each stellar model using the equation
of state of \cite{Lattimer_Swesty__1991__NuclearPhysicsA__LS-EOS} with
an incompressibility of $K = 220 \, \mathrm{MeV}$ (LS220) and added
comparison simulations with the SFHo EOS
\cite{Steiner_et_al__2013__apj__Core-collapseSupernovaEquationsofStateBasedonNeutronStarObservations}
and the GShen EOS 
\cite{Shen_et_al__2011__prc__Newequationofstateforastrophysicalsimulations}
for the {progenitor} with $M_{\mathrm{ZAMS}} = 15 \, \Msol$. To this set of
simulations, we add the waveform of a two-dimensional model used in
\cite{Torres:2019a}, denoted \texttt{s20S}. It corresponds to a star
with the same initial mass, $M_{\mathrm{ZAMS}} = 20 \, \Msol$, as for
one of the other 7 axisymmetric simulations, but was taken from a
newer set of stellar-evolution models
\cite{Woosley_Heger__2007__physrep__Nucleosynthesisandremnantsinmassivestarsofsolarmetallicity}.
It was evolved with the SFHo EOS.
